---
title: "CodeBook.md"
author: "Ludi Akue (Lietwin)"
date: "June 23, 2015"
output: html_document
---

## Variables created 

### Data objects
Each type of data is handled through four types of data objects corresponding to four different prefixes :
- train-*: data object for the _train_ data measurements
- test-*: data object for the _test_ data measurements
- all-*: data object for the merge of _train_ and _test_ measurements
- tidy-*:  tidy data object with descriptive labels (in tbl_df format)

- For the features measurements 
    - trainfeat
    - testfeat
    - allfeat
    - tidyfeat        
```{r}
str(tidyfeat)
```

- For the activities measurements 
    - trainact
    - testact
    - allact
    - tidyact
```{r}
str(tidyact)
```

- For the subjects measurements 
    - trainsubject
    - testsubject
    - allsubject
    - tidysubject
```{r}
str(tidysubject)
```
    
- labels, features and activities
    - features_dic
    - activity_dic
```{r}
str(features_dic)
str(features_dic)
```
    
- The newly created tidy data set
    - tidynew
    - the corresponding file name tidydata.txt
```{r}
str(tidynew)
```

```{r}
tidynew
```

### Other variables used

- files paths : all the variables ending in "file"
    - trainfeatfile:  "UCI_HAR_data/train/X_train.txt"
    - testfeatfile: "UCI_HAR_data/test/X_test.txt"
    - trainactfile:  "UCI_HAR_data/train/y_train.txt"
    - testactfile: "UCI_HAR_data/test/y_test.txt"
    - trainsubjectfile: "UCI_HAR_data/train/subject_train.txt"
    - testsubjectfile: "UCI_HAR_data/test/subject_test.txt"
    - featuresfile: "UCI_HAR_data/features.txt"
    - activitiesfile: "UCI_HAR_data/activity_labels.txt"
